---
title: "R Notebook"
output: html_notebook
---

# Load libraries 

```{r}
library(ggplot2)
library(tidyverse)
library(readr)
library(ggrepel)
library(rstatix)
library(readxl)
library(openxlsx)
library(jsonlite)

```

```{r}
calc_correlation <- function(data,x,y){
  
  #calculate correlations
  pearson_correlation <-cor.test(x= data[[x]], y= data[[y]], method = c( "pearson"))
  spearman_correlation <-cor.test(x= data[[x]], y= data[[y]], method = c( "spearman"))
  
	correlation_table <- tibble(x=  x,
	                            y= y,
	                            test = c("pearson", "spearman"),
	                            correlation_coef = c(pearson_correlation$estimate, spearman_correlation$estimate),
	                            p_value = c(pearson_correlation$p.value, spearman_correlation$p.value))

	return(correlation_table)
	
  
}
```


# Load metadata
```{r}


metadata_path <- "../metadata/metadata.xlsx"
metadata_gov_path <- "../metadata/metadata_gov.xlsx"

metadata <- readxl::read_xlsx(metadata_path)
metadata_gov <- readxl::read_xlsx(metadata_gov_path)


```

# Load data
```{r}

#Set attack date
attack_date <- as.POSIXct("2023-10-07 06:00:00", tz = "UTC")

#List of retired members
ret_members <- c("replouiegohmert", "repkevinbrady", "jimlangevin","reppeterdefazio", "repmondaire", "repfredupton", "repseanmaloney","repmeijer","repspeier", "repmobrooks")

#Load and tidy data
data_numeric <- read_excel("../data/all_data_us__updated_to_2023-12-19__11_13.xlsx")%>%
  select(-country , -conflict_sentiment)%>%
  rename(conflict_sentiment = conflict_sentiment_v)%>%
  mutate(conflict_sentiment = as.numeric(conflict_sentiment),
         conflict_sentiment_chr = case_when(conflict_sentiment == 0 ~ "not_related",
                                            conflict_sentiment == 1 ~ "pro_palestinian",
                                            conflict_sentiment == 2 ~ "complex_attitude",
                                            conflict_sentiment == 3 ~ "pro_israeli",
                                            conflict_sentiment == 9 ~ "ambiguous"),
         conflict_sentiment_chr = factor(conflict_sentiment_chr, 
                                         levels = c("not_related","ambiguous", "pro_palestinian", "complex_attitude", "pro_israeli")),
         is_conflict_related = if_else(conflict_sentiment == 0, true = "not_related", false = "conflict_related"),
         conflict_sentiment_rank = case_when(conflict_sentiment == 1 ~ -1,
                                            conflict_sentiment == 2 ~ 0,
                                            conflict_sentiment == 3 ~ 1),
         day = as.Date(upload_date),
         day_of_week = wday(upload_date),
        n_week_from_7_10 = difftime(upload_date, attack_date, units = "weeks"),
        n_week_from_7_10 = round(as.numeric(n_week_from_7_10))
        )%>%
  # Fix names
  mutate(username =  str_to_lower(username),
        username = if_else(username == "ossoff" ,true = "senossoff", false = username),
         username = if_else(username == "claudiatenney", true = "reptenney", false = username),
         username = if_else(username == "repschakowsky", true = "janschakowsky", false = username),
        username = if_else(username == "rudyyakym", true = "reprudyyakym", false = username),
        username = if_else(username == "patryanuc", true = "reppatryanny",  false = username),
        username = if_else(username == "michaelgwaltz", true = "repwaltzpress", false = username),
        username = if_else(username == "marypeltola", true = "rep_peltola", false = username),
        username = if_else(username == "aoc", true = "repaoc", false = username),
        username = if_else(username == "leadermcconnell", true = "senatemajldr", false = username),
        username = if_else(username == "anthonydespo", true = "repdesposito", false = username),
        username = if_else(username == "teamcmr", true = "cathymcmorris", false = username),
        username = if_else(username == "summerforpa", true = "repsummerlee", false = username),
        username = if_else(username == "rokhanna", true = "reprokhanna", false = username),
        username = if_else(username == "senlaphonza", true = "laphonzab", false = username),
        username = if_else(username == "jeffjacksonnc", true = "repjeffjackson", false = username),
        username = if_else(username == "jaredemoskowitz", true = "repmoskowitz", false = username)
        )%>%
  # remove data from retired members
  filter(!(username %in% ret_members))%>%
  rename_all(~str_replace_all(tolower(.), " ", "_"))%>%
  # remove users of goverment
  filter(!(username %in% metadata_gov$username))

# Calculate distance from latest time point
last_data_point <- data_numeric%>%
  slice_max(day)%>%
  pull(day)%>%
  unique()

print(last_data_point)

data_numeric <- data_numeric%>%
  mutate(diff_from_latest_datapoint = as.numeric(difftime(day, last_data_point, units = "days")))

```


# General statistics

## Tweet frequncy
Calculate genral statistics:
1. number of conflict related tweets per day
2. number of conflict related tweets per person

```{r}
# Total number of tweets per day
ggplot(data_numeric, aes(x = day, fill = is_conflict_related))+
  geom_bar()+
  theme_minimal(base_size =15)+
  labs(x = "Date", y = "Number of members", title = "Number of tweets per day")

# Number of users tweeted per day
data_numeric%>%
  filter(is_conflict_related == "conflict_related")%>%
  select(username, day,is_conflict_related)%>%
  unique()%>%
  count(day, is_conflict_related)%>%
  ggplot(aes(x = day, y = n, fill = is_conflict_related))+
  geom_col()+
  theme_minimal(base_size =15)+
  labs(x = "Date", y = "Number of members", title = "Number of tweeting members per day - conflict related")

```

## Class statistics
```{r fig.height=2.5, fig.width=5}

#Overall is_conflict_related count
ggplot(data_numeric, aes(y = is_conflict_related))+
  geom_bar(stat = "count", aes(fill = is_conflict_related))+
  geom_text(stat = "count", aes(label = stat(count)), hjust =1, color = "white")+
  theme_bw(base_size = 15)+
  labs(x = "Count", y = "is conflict related")+
    theme(legend.position = "none")+
  scale_fill_manual(values = c("grey20", "grey80"))

#Overall conflict_sentiment count
data_numeric%>%
  filter(conflict_sentiment != 0)%>%
  filter(conflict_sentiment != 9)%>%
  count(conflict_sentiment_chr)%>%
  ggplot(., aes(y = conflict_sentiment_chr, x= n))+
  geom_col(aes(fill = conflict_sentiment_chr), color = "black", size = 0.5)+
  geom_text( aes(label = n), hjust =0, color = "black")+
  theme_bw(base_size = 15)+
  labs(x = "Count", y = "Sentiment")+
  scale_fill_manual(values = c("#e08214", "#ffffbf", "#5aae61"))+
  theme(legend.position = "none")+
  xlim(c(0,8500))

```

## Tweet class overtime
```{r}
#Number of tweets per day & sentiment
data_numeric%>%
  filter(is_conflict_related == "conflict_related")%>%
  filter(conflict_sentiment != 9)%>%
  count(conflict_sentiment_chr, day_est)%>%
  ggplot(aes(x = day_est, y = n,fill = conflict_sentiment_chr))+
  geom_col(color = "grey30")+
  theme_minimal(base_size = 12)+
  labs(x= "Date", y = "Tweet count")+
  theme(legend.position = "none")+
  scale_fill_manual(values = c("#e08214", "#ffffbf", "#5aae61"))


#Frequency of tweets per day & sentiment
freq_sentiment <- data_numeric%>%
  filter(is_conflict_related == "conflict_related")%>%
    # filter(conflict_sentiment != 9)%>%
  left_join(metadata)%>%
  filter(legislation_body != "goverment")%>%
  count(conflict_sentiment_chr, day, party)%>%
  pivot_wider(names_from = conflict_sentiment_chr, values_from = n, values_fill = 0)%>%
  mutate(total = pro_palestinian+complex_attitude+pro_israeli+ambiguous,
         freq_pro_palestinian = pro_palestinian/total,
         freq_complex_attitude = complex_attitude/total,
         freq_pro_israeli = pro_israeli/total,
         freq_ambiguous = ambiguous/total)%>%
  select(day, freq_pro_palestinian, freq_complex_attitude, freq_pro_israeli,freq_ambiguous, party)%>%
  rename(pro_palestinian = freq_pro_palestinian, 
         complex_attitude= freq_complex_attitude,
         pro_israeli = freq_pro_israeli,
         ambiguous = freq_ambiguous)%>%
  pivot_longer(-c(day, party), names_to = "sentiment", values_to = "freq")%>%
  mutate(sentiment = factor(sentiment, levels= c("ambiguous", "pro_palestinian", "complex_attitude", "pro_israeli")))

#plot
freq_sentiment%>%
  ggplot(., aes(x = day, y = freq, fill = sentiment))+
  geom_col()+
  scale_fill_manual(values = c("grey90", "#e08214", "#ffffbf", "#276419"))+
  theme_minimal(base_size = 15)+
  labs(x = "Date", y = "Relative abundence (%)")+
  facet_wrap(~party, ncol = 1)


```
## Time of latest tweet

```{r}
last_data_point <- data_numeric%>%
  slice_max(day)%>%
  pull(day)%>%
  unique()

time_of_last_tweet <- data_numeric %>%
  filter(is_conflict_related == "conflict_related") %>%
  filter(conflict_sentiment!=9) %>%
  group_by(username)%>%
  slice_max(day)%>%
  ungroup()%>%
  mutate(diff_time = abs(as.numeric(difftime(day, last_data_point, units = "days"))),
         diff_group = case_when(diff_time<=7 ~ "week",
                                diff_time>7 & diff_time<=30 ~ "month",
                                diff_time> 30 ~ "longer than month"))%>%
  left_join(metadata)%>%
  mutate(progressive = if_else(username %in% metadata_d_party$username & party == "Democratic", 
                               true = "progressive",
                               false = "not_progressive"))
```

# Member-party level analysis

## Intrest overtime

```{r}

# Calculate interst
temporal_intrest <- data_numeric%>%
  left_join(metadata, join_by = "username")%>%
  count(day, party, is_conflict_related, day_of_week, legislation_body)%>%
  pivot_wider(names_from = is_conflict_related, values_from = n)%>%
  mutate(intrest = conflict_related/(conflict_related+not_related),
         total_n = conflict_related+not_related,
         is_weekend = if_else(day_of_week %in% c(6,7), true = 1, false = 0),
         diff_from_0710 = as.numeric(day - as.Date("2023-10-07")))

# Plot
ggplot(temporal_intrest, aes(x = day, y = intrest, color = party))+
  geom_smooth(fill = "grey70", method = "lm")+
  geom_point(size = 3, alpha = 0.75)+
  theme_minimal(base_size = 15)+
  scale_color_manual(values = c("#457b9d", "#e63946"), "Party")+
  labs(x= "Date", y = "Intrest")+
  facet_wrap(~legislation_body, ncol = 1)

# Linear regression modeling & correlation
temporal_intrest%>%
  filter(day >= as.POSIXct("2023-12-01 00:00:00"))%>%
  lm(., formula = intrest~day + is_weekend + legislation_body + party)%>%
  summary()

temporal_intrest%>%
  filter(day >= as.POSIXct("2023-12-01 00:00:00"))%>%
  calc_correlation(., x= "intrest", y="diff_from_0710")

```
## Intrest internal\external
freq of 9 vs 1/2/3 from all conflict_related tweets

```{r}

#Orgenize data
temporal_intrest_external <- data_numeric%>%
  filter(day >= as.POSIXct("2023-11-05 00:00:00"))%>%
  filter(is_conflict_related == "conflict_related")%>%
  left_join(metadata, join_by = "username")%>%
  mutate(external_internal = if_else(conflict_sentiment == 9,  true ="intrnal", false = "external"))%>%
  count(day, external_internal)%>%
  pivot_wider(names_from = external_internal, values_from = n)%>%
  mutate(freq_internal = 100*intrnal/(intrnal+external),
         total_n = intrnal+external,
         diff_from_0710 = as.numeric(day - as.Date("2023-10-07")))
  
# Regression model & correlation
temporal_intrest_external%>%
  lm(., formula = freq_internal~day)%>%
  summary()

calc_correlation(temporal_intrest_external, x= "freq_internal", y="diff_from_0710")

# Plot
ggplot(temporal_intrest_external, aes(x= day, y = freq_internal))+
  geom_smooth(method = "lm", color = "grey20", fill = "grey90")+
  geom_point(size = 4, alpha = 0.75, color = "#0A9396")+
  theme_minimal(base_size = 15)+
  labs(x= "Date", y = "Domestic policy(%)", 
       title = "Increased discussion on domestic policy aspects")

```

## House and party position

```{r fig.width=14, fig.height=7}

# Calculate summery statistics per user

user_summery_stat <- data_numeric%>%
  group_by(username)%>%
  summarise(mean_like_amount = mean(like_amount),
            mean_retweet = mean(retweet_amount),
            mean_comments = mean(comments_amount),
            n_tweet = n())

# User interest in Israel
user_intrest <- data_numeric%>%
  group_by(username, is_conflict_related)%>%
  summarise(n = n())%>%
  ungroup()%>%
  pivot_wider(names_from = is_conflict_related, values_from  = n, values_fill = 0)%>%
  mutate(intrest = conflict_related / (conflict_related + not_related))

# User sentiment to Israel
user_sentiment <- data_numeric%>%
  filter(is_conflict_related == "conflict_related")%>%
  filter(conflict_sentiment != 9)%>%
  group_by(username)%>%
  summarise(mean_sentiment = mean(conflict_sentiment_rank),
            mode_sentiment = mode(conflict_sentiment_rank))

user_summery_stat <- user_summery_stat%>%
  left_join(user_sentiment, by = "username")%>%
  left_join(user_intrest, by= "username")%>%
  left_join(metadata, by= "username")%>%
  mutate(text_for_plot = if_else(mean_sentiment<0, true = full_name, false = ""))

# Plot interest and sentiment
user_summery_stat%>%
  filter(legislation_body != "government")%>%
  ggplot(., aes(x = mean_sentiment, y = intrest ))+
  geom_vline(xintercept = 0, size = 1.5, color = "grey30")+
  geom_point(alpha = 0.5, aes(fill = mean_sentiment, size = n_tweet), color = "black", shape = 21)+
  theme_minimal(base_size = 20)+
  scale_fill_distiller(palette = "RdYlBu", direction = 1)+
  labs(y = "Intrest", x = "Sentiment")+
  facet_grid(vars(legislation_body),vars(party))+
  geom_label_repel(aes(label = text_for_plot))

```


## Latest position
Here we map the postion of members according to their last tweet
```{r}
# Find there last position in every timepoint
date_list <- data_numeric%>%
  distinct(day)%>%
  pull()

latest_position <- map(.x = date_list,
    .f = ~{
      results <- data_numeric%>%
        filter(is_conflict_related == "conflict_related")%>%
        filter(conflict_sentiment != 9)%>%
        filter(day<=.x)%>%
        group_by(username)%>%
        slice_max(upload_date)%>%
        ungroup()%>%
        left_join(metadata, by = "username")%>%
        filter(legislation_body != "goverment")%>%
        count(conflict_sentiment_chr, party, legislation_body)%>%
        mutate(day = .x)%>%
      return(results)
    })%>%
  bind_rows()

#Plot all
ggplot(latest_position, aes(x = day, y = n))+
  geom_col(aes(fill = conflict_sentiment_chr), color = "grey10")+
  theme_minimal(base_size = 15)+
  scale_fill_manual(values = c("#e08214", "#ffffbf", "#5aae61"), "latest sentiment")+
  labs(x = "Date", y = "Number of members")+
  facet_grid(cols = vars(party), rows = vars(legislation_body))

# Regression model

latest_position%>%
  filter(party == "Democratic")%>%
  filter(legislation_body == "House of Representatives",
         conflict_sentiment_chr  == "pro_palestinian")%>%
  filter(day >= as.POSIXct("2023-12-01"))%>%
  mutate(distance_in_days  = abs(as.numeric(difftime(attack_date, day, units = "days"))))%>%
  lm(formula = n~distance_in_days, data = .)%>%
  summary()


```

# Others 

## Appearance of pro_palestinian agenda
When is the first time that member post tweet with class 1
```{r}

# Find the first date in which a member post tweet with class 1
first_pro_p_tweet <- data_numeric%>%
  left_join(metadata, by = "username")%>%
  filter(party == "Democratic")%>%
  filter(conflict_sentiment_chr == "pro_palestinian")%>%
  group_by(username)%>%
  slice_min(upload_date, n = 1)%>%
  ungroup()

tmp <- first_pro_p_tweet%>%
  count(day)%>%
  mutate(cumsum = cumsum(n))
         
n_pro_p_members <- tibble(day = seq(min(tmp$day), last_data_point, by = "days"))%>%
  left_join(tmp, by = "day")%>%
  mutate(cumsum = if_else(is.na(cumsum), true = lag(cumsum), false = cumsum))%>%
  fill(cumsum, .direction = "up")

# Plot
ggplot(n_pro_p_members, aes(x = day, y = cumsum))+
  geom_col(color = "white")+
  theme_minimal(base_size =15)+
  labs(y = "# Congress members", x = "Date", title = "Cumulative number of members with a pro-palstenian tweet")+
  geom_text(aes(label = cumsum), size =3, vjust = -0.2)

```

## Appearance of complex agenda
When is the first time that member post tweet with class 2

```{r}
first_complex_tweet <- data_numeric%>%
  filter(conflict_sentiment_chr == "complex_attitude")%>%
  group_by(username)%>%
  slice_min(upload_date, n = 1)%>%
  ungroup()%>%
  left_join(metadata)

count_per_day_complex <- first_complex_tweet%>%
  count(day, party, legislation_body)%>%
  group_by(party, legislation_body)%>%
  mutate(cum_n = cumsum(n))%>%
  ungroup()

ggplot(count_per_day_complex, aes(x = day, y = cum_n, color = party))+
  geom_point(size = 3)+
  geom_line()+
  theme_minimal(base_size =15)+
  labs(y = "# Congress members", x = "Date")+
  geom_vline(xintercept = 13, linetype= "dashed", color = "grey30", size = 0.75)+
  geom_vline(xintercept = 17, linetype= "dashed", color = "grey30", size = 0.75)+
  scale_color_manual(values = c("#457b9d", "#e63946"), "Party")+
  facet_wrap(~legislation_body, ncol = 1, scale = "free")

```

## Examples from specific users
```{r fig.width=9, fig.height=4}

spacific_user <- "repbeccab"


tmp <- data_numeric%>%
  filter(username == spacific_user)%>%
  filter(is_conflict_related == "conflict_related")%>%
  filter(conflict_sentiment != 9)%>%
  select(day, conflict_sentiment_chr)

data_for_plot <- ratio_across_dates_sum%>%
  filter(username == spacific_user)%>%
  filter(date %in% tmp$day)%>%
  left_join(tmp, by = c("date" = "day"))

ggplot(data_for_plot, aes(x = date, y=sentiment))+
  geom_line(size = 3, color = "grey80", alpha = 0.5)+
  geom_point(size = 4, shape = 21, aes(fill = conflict_sentiment_chr))+
  theme_minimal(base_size = 15)+
  labs(x = "Date", y = "Sentiment", title = "Becca Balint")+
  ylim(c(-1, 1))+
  scale_fill_manual(values = c("#e08214", "#ffffbf", "#276419"), "Sentiment")

```